Ensemble Stability of Biological Networks

### 2014-09-17 paper.tex
add commands to header
add stability figure and combined stability regions figure

% \def\wprod{\mathrm{wp}}
Next, we introduce two basic functors from $\Path (G)$.  One of these is
$\length \colon \Path(G) \to \mathbb{N}$ (regarding the natural numbers
as a category with a single object) which sends each path to its length.
The other functor is the weight product functor.  Given an assignement 
$w \colon \Path(G) \to \mathbb(R)$ of weights to the edges of our digraph,
define $\wprod \colon \Path(G) \to \mathbb{R}$ to be the function which sends
each path to the product of the weights associated to the edges which
that path traverses.  Given the way that graphs are associated to matrices,
weights on edges correspond to matrix entries and, given a path 
$v_1, v_2, v_3 \ldots$, we have $\wprod(v_1, v_2, v_3 \ldots) =
m_{v_1 v_2} m_{v_2 v_3} \cdots$.  Going in the opposite direction, we
note that any functor from $\Path(G)$ to $\mathbb{R}$ may be regarded as
a weighted product for a suitable choice of weights.  We extend $\wp$ to
$\mathcal{A}(G)$ by linearity; the result is an algebra homomorphism.

@@

The probability of \emph{a priori} stability and of stability to perturbations for all two component systems is given in Table \ref{tab:structstabmat}. Similarly, the analogous results for all three component systems is given in Table \ref{tab:structstabmat3}.

@@

\section{Connectivity is correlated with robustness}
\ref{fig:stab3x3} shows the probability of stability to perturbations for all three component systems as a function of connectivity.

>>>>

Next, we introduce two basic functors from $\Path (G)$.  One of these is
$\length \colon \Path(G) \to \mathbb{N}$ (regarding the natural numbers
as a category with a single object) which sends each path to its length.
The other functor is the weight product functor.  Given an assignement
$w \colon \Path(G) \to \mathbb(R)$ of weights to the edges of our digraph,
define $\wprod \colon \Path(G) \to \mathbb{R}$ to be the function which sends
each path to the product of the weights associated to the edges which
that path traverses.  Given the way that graphs are associated to matrices,
weights on edges correspond to matrix entries and, given a path
$v_1, v_2, v_3 \ldots$, we have $\wprod(v_1, v_2, v_3 \ldots) =
m_{v_1 v_2} m_{v_2 v_3} \cdots$.  Going in the opposite direction, we
note that any functor from $\Path(G)$ to $\mathbb{R}$ may be regarded as
a weighted product for a suitable choice of weights.  We extend $\wp$ to
$\mathcal{A}(G)$ by linearity; the result is an algebra homomorphism.

@@

The probability of \emph{a priori} stability and of stability to perturbations for all two component systems is given in Table \ref{tab:structstabmat}. Similarly, the analogous results for all three component systems is given in \ref{tab:structstabmat3} and \ref{fig:stab3x3}. It has been stated previously on the basis of simulation that system stability decreases with connectivity as the system size goes to infinity \cite{May1972}. For small system sizes such as the two and three component systems, studied here the situation is not so clear cut. For two component systems, system stability is constant across the entire range of connectivities. For three component systems, the trend is unclear as shown in \ref{fig:apstab3x3}.

@@

\section{Connectivity is correlated with robustness}
The relationship between connectivity and probability of stability to perturbations for two component systems is shown in \ref{tab:structstabmat}. Likewise, \ref{fig:stab3x3} and \ref{tab:structstabmat3} show the probability of stability to perturbations for all three component systems as a function of connectivity.

### 2014-09-17 tex/figures.tex
add stability figure and combined stability regions figure

@@

>>>>

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.5\columnwidth]{fig/region2and3.pdf}
\caption{{\bf Stability conditions on coefficients of the characteristic polynomial for two and three component systems.} The regions correspond to all possible relationships between the invariants determined by the characteristic polynomial.}
\label{fig:region2and3}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\noindent\includegraphics[width=0.8\columnwidth]{fig/apstab3x3.pdf}
\caption{{\bf Plot of stability versus connectivity for three component systems.} }
\label{fig:apstab3x3}
\end{figure}
